TCC Senai Cimatec

### 2022-12-18 sections/cover.tex
Add title to professors

    \begin{flushright}
        Brenda Silva de Alencar\textsuperscript{1}\\
        Felipe Mohr Santos Muniz Barreto\textsuperscript{2}\\
        Lucas Lins Souza\textsuperscript{3}\\
        Orientador: Paulo Andrade Souza\textsuperscript{4}\\
        Coorientador: Marco Antônio dos Reis\textsuperscript{5}\\
    \end{flushright}
    \begin{flushleft}
      \begin{small}
          \textsuperscript{1}Instituição: Centro Universitário SENAI CIMATEC, E-mail: brenda.s1602@outlook.com;\\
          \textsuperscript{2}Instituição: Centro Universitário SENAI CIMATEC, E-mail: felipe18mohr@gmail.com;\\
          \textsuperscript{3}Instituição: Centro Universitário SENAI CIMATEC, E-mail: lucaslinssouza@gmail.com;\\
          \textsuperscript{4}Instituição: Centro Universitário SENAI CIMATEC, E-mail: paulo.andrade@fieb.org.br;\\
          \textsuperscript{5}Instituição: Centro Universitário SENAI CIMATEC, E-mail: marcoreis@me.com;\\      
        \end{small}
      \end{flushleft}

>>>>

    \begin{flushright}
        Brenda Silva de Alencar\textsuperscript{1}\\
        Felipe Mohr Santos Muniz Barreto\textsuperscript{2}\\
        Lucas Lins Souza\textsuperscript{3}\\
        Orientador: MSc. Paulo Andrade Souza\textsuperscript{4}\\
        Coorientador: MSc. Marco Antônio dos Reis\textsuperscript{5}\\
    \end{flushright}
    \begin{flushleft}
      \begin{small}
          \textsuperscript{1}Instituição: Centro Universitário SENAI CIMATEC, E-mail: brenda.s1602@outlook.com;\\
          \textsuperscript{2}Instituição: Centro Universitário SENAI CIMATEC, E-mail: felipe18mohr@gmail.com;\\
          \textsuperscript{3}Instituição: Centro Universitário SENAI CIMATEC, E-mail: lucaslinssouza@gmail.com;\\
          \textsuperscript{4}Instituição: Centro Universitário SENAI CIMATEC, E-mail: paulo.andrade@fieb.org.br;\\
          \textsuperscript{5}Instituição: Centro Universitário SENAI CIMATEC, E-mail: marcoreis@me.com;\\      
        \end{small}
      \end{flushleft}
